Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS

### 2022-04-11 outputs/paper/paper.Rmd
Update paper.Rmd

Was any preprocessing/cleaning/labeling of the data done?
- The data was originally obtained in PDF format. The table from the survey PDF was converted to a usable data frame in R using the library pdftools for R. 
Was the “raw” data saved in addition to the preprocessed/cleaned/labeled data (e.g., to support unanticipated future uses)?
-The raw data obtained is saved in outputs/data/raw_data_male.csv and outputs/data/raw_data_female.csv
Is the software that was used to preprocess/clean/label the data available?
-R software is available at https://www.R-project.org/

>>>>

Was any preprocessing/cleaning/labeling of the data done?
- The data was originally obtained in PDF format. The table from the survey PDF was converted to a usable data frame in R using the library pdftools for R. 
Was the “raw” data saved in addition to the preprocessed/cleaned/labeled data (e.g., to support unanticipated future uses)?
- The raw data obtained is saved in outputs/data/raw_data_male.csv and outputs/data/raw_data_female.csv
Is the software that was used to preprocess/clean/label the data available?
- R software is available at https://www.R-project.org/
